MSF_Groupwork-NBA_shotlog

### 2016-10-09 MSFGroupwork-NBAHotHand.Rmd

###Introduction
I   What is your theme or research question?
a. Hot Hand Theory  
b. Defender Proximity Analysis (Reza)
c. Shot Clock Pressure  (Alex)
d. Close Game Effect - Small Margin affecting the scoring rate  
e. Home Advantage (Alex is working in this point)  
f. Fatigue Effect (Quarter Heat Rate)  
g. Shooting Percentage (James)
h. Fatigue Effect (Number of Rest Day)  
i.

@@

```{r}
#adding columns for names of 'home' and 'away' teams
df[,"MATCHUP"] <- as.character(df[,"MATCHUP"])

for (i in 1:nrow(df)) {
  if (LOCATION[i]=="H") {df$HOME_TEAM [i] <- unlist(strsplit(df$MATCHUP[i]," "))[5]
  df$AWAY_TEAM [i] <- unlist(strsplit(df$MATCHUP[i]," "))[7]
  if (W[i]==1) df$WINNER[i] <- "HOME" 
  if (W[i]==0) df$WINNER[i] <- "AWAY"}
  if (LOCATION[i]=="A") {df$HOME_TEAM [i] <- unlist(strsplit(df$MATCHUP[i]," "))[7] 
  df$AWAY_TEAM [i] <- unlist(strsplit(df$MATCHUP[i]," "))[5]
  if (W[i]==0) df$WINNER[i] <- "HOME"  
  if (W[i]==1) df$WINNER[i] <- "AWAY"}}

@@

```{r}
#combining columns for the analysis
library(reshape)
dfwl<- cast(df, GAME_ID1 + HOME_TEAM + AWAY_TEAM + WINNER ~ LOCATION)
dfwl[,"WINNER"] <- as.character(dfwl[,"WINNER"])

for (i in 1:nrow(dfwl)) { 
if (dfwl$WINNER[i]=="HOME") dfwl$WINNER2[i]<-1
if (dfwl$WINNER[i]=="AWAY") dfwl$WINNER2[i]<-2}
```

```{r}
dfwl2<-cast(dfwl, HOME_TEAM ~ WINNER)
dfwl2<- dfwl2[,c(1,3,2)]
dfwl2$WIN_PCT<- round(dfwl2$HOME/(dfwl2$HOME+dfwl2$AWAY),2)

for (i in 1:nrow(dfwl2)) {
if(dfwl2$WIN_PCT[i]>0.5) dfwl2$HOMEADV[i]<- "YES" else dfwl2$HOMEADV[i]<- "NO"}

dfwl2<- dfwl2[order(dfwl2$WIN_PCT),]; dfwl2

library(ggplot2)
ggplot(dfwl2, aes(x=HOME_TEAM,y=WIN_PCT,col=HOMEADV))+ geom_point()
```

>>>>

###Introduction
I   What is your theme or research question?
a. Hot Hand Theory (Artemis)
b. Defender Proximity Analysis (Reza)
c. Shot Clock Pressure  (Alex)
d. Close Game Effect - Small Margin affecting the scoring rate  
e. Home Advantage (Alex is working in this point)  
f. Fatigue Effect (Quarter Heat Rate)  
g. Shooting Percentage (James)
h. Fatigue Effect (Number of Rest Day)  
i.

@@

```{r}
#adding columns for names of 'home' and 'away' teams. In addition, WINNER column tells which team won
df[,"MATCHUP"] <- as.character(df[,"MATCHUP"])
df[,"W"] <- as.character(df[,"W"])

for (i in 1:nrow(df)) {
  if (LOCATION[i]=="H") {df$HOME_TEAM [i] <- unlist(strsplit(df$MATCHUP[i]," "))[5]
  df$AWAY_TEAM [i] <- unlist(strsplit(df$MATCHUP[i]," "))[7]
  if (W[i]=="W") df$WINNER[i] <- "HOME" 
  if (W[i]=="L") df$WINNER[i] <- "AWAY"}
  if (LOCATION[i]=="A") {df$HOME_TEAM [i] <- unlist(strsplit(df$MATCHUP[i]," "))[7] 
  df$AWAY_TEAM [i] <- unlist(strsplit(df$MATCHUP[i]," "))[5]
  if (W[i]=="L") df$WINNER[i] <- "HOME"  
  if (W[i]=="W") df$WINNER[i] <- "AWAY"}}

@@

```{r}
aa<- cast(df, GAME_ID1 + HOME_TEAM + AWAY_TEAM + WINNER ~ W)

table(aa$WINNER) [2]
#home wins:
hh<-sum(aa$WINNER=="HOME")
#Away wins:
aw<-sum(aa$WINNER=="AWAY")
#percentage of home team winning: 
round(hh/(hh+aw),2)
```

```{r}
head(aa)
aa1<- cast(aa, HOME_TEAM  ~ WINNER); names(aa1)[1]<-"TEAM"
aa1$WIN_PCT_HOME<-round(aa1$HOME/(aa1$HOME+aa1$AWAY),2)

aa2<- cast(aa, AWAY_TEAM ~ WINNER); names(aa2)[1]<-"TEAM"
aa2$WIN_PCT_AWAY<-round(aa2$HOME/(aa2$HOME+aa2$AWAY),2)

aa3<- merge (aa1,aa2, by ="TEAM")
for (i in 1:nrow(aa3)) {if(aa3$WIN_PCT_HOME[i]>aa3$WIN_PCT_AWAY[i]) aa3$HOME_ADV[i]<-"YES" else aa3$HOME_ADV[i]<-"NO"}
head(aa3)

ggplot(aa3,aes(x=TEAM, y= WIN_PCT_HOME, col= HOME_ADV))+ geom_point()
#TO BE UPDATED
```
